Challenges and Solutions of Developing and Implementing a Novel Desktop-as-a-Service

### 2024-05-10 paper.tex
Change delay in chapter 'Internal Processing and Communication[1~#

Allthough we can not yet provide a full-fledged performance analysis,
we already measured promising results in our local test environment.
Depending on the exact setup,
the solution provides
reasonable round-trip times and delays for each communication direction
visualized in figure~\ref{perf_internal_communication}.
In a minimal setup, we measured delays of around 10ms for client communication,
below 1ms for internal backend communication
but up to 1000ms for instance communication.
But these numbers are only rough estimates
as certain optimization concepts remain to be implemented.

>>>>

Allthough we can not yet provide a full-fledged performance analysis,
we already measured promising results in our local test environment.
Depending on the exact setup,
the solution provides
reasonable round-trip times and delays for each communication direction
visualized in figure~\ref{perf_internal_communication}.
In a minimal setup, we measured delays of around 10ms for client communication,
around 100ms for internal backend communication
but up to 1000ms for instance communication.
But these numbers are only rough estimates
as certain optimization concepts remain to be implemented.
% Explanation delays: Half-way of a Roundtrip.
% We state 1000ms for instance-communication (500ms per connection, we make two, so 1000ms)
% We state 100ms for internal comm, which is a roundtrip of 200ms for auth divided by two, so 100ms
% 10ms for client delay we can take a clientside timestamp when sending request and a server side timestamp when the request is intially received.
% So we directly measure a deley, no rtt. The delay varias between 9 and 14ms, so we state roughly 10ms.
% In my newest tests this number goes up to 50ms, but thats ok for what we receive in advance.
